Public transport and school location impacts on educational inequalities: insights from São Paulo

### 2017-04-02 paper_v2.tex
Add sentence to abstract

\begin{abstract}
In many large Latin American urban areas such as the São Paulo
Metropolitan Region (SPMR), growing social and economic inequalities are embedded through high spatial inequality in the provision of state schools and affordable public transport to these schools. This paper sheds light on the transport-education inequality nexus with reference to school accessibility in the SPMR. 
To assess school accessibility, we develop an accessibility index which combines information on the spatial distribution of adolescents, the location of existing schools, and the public transport provision serving the school catchment area into a single measure. The index is used to measure school accessibility locally across 633 areas within the SPMR. We use the index to simulate the impact of a policy aiming at increasing the centralization of public secondary education provision, and find that it negatively affects students with the lowest levels of accessibility. These results illustrate how existing inequalities are amplified by variable accessibility to schools across income groups and geographical space.
\end{abstract}

>>>>

\begin{abstract}
In many large Latin American urban areas such as the São Paulo
Metropolitan Region (SPMR), growing social and economic inequalities are embedded through high spatial inequality in the provision of state schools and affordable public transport to these schools. This paper sheds light on the transport-education inequality nexus with reference to school accessibility in the SPMR. 
To assess school accessibility, we develop an accessibility index which combines information on the spatial distribution of adolescents, the location of existing schools, and the public transport provision serving the school catchment area into a single measure. The index is used to measure school accessibility locally across 633 areas within the SPMR. We use the index to simulate the impact of a policy aiming at increasing the centralization of public secondary education provision, and find that it negatively affects students with the lowest levels of accessibility. These results illustrate how existing inequalities can be amplified by variable accessibility to schools across income groups and geographical space.
The research suggests that educational inequality impacts of school agglomeration policies should be considered before centralisation takes place and highlights the links between transport planning social injustice that.
\end{abstract}
